%\chapter*{ACKNOWLEDGMENT}
\begin{center}
{\bf ACKNOWLEDGMENT}\\[24pt]
\end{center}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENT}
{\baselineskip=1.5\baselineskip

We would like to express our sincere gratitude to the following people and institutions which, in one way or another, greatly contributed towards the completion of this study. 

To our adviser \textbf{\textit{\adviser}} for painstakingly checking every detail of this paper. We are extremely thankful and indebted to you Sir for sharing your expertise and valuable guidance. Had it not been for your encouragement and moral support, this endeavor would surely have fallen into complete obscurity.

To our panel members, \textbf{\textit{\deptchair}}, \textbf{\textit{\panelone}}, \textbf{\textit{\paneltwo}}, and \textbf{\textit{\panelthree}} for sharing your knowledge and diligently spending your time in giving valuable insights, corrections and suggestions for the betterment of this study. We have high regards for both of you.

To the faculty and staff of the \textbf{\textit{Department of Computer Engineering}} for your encouragement and support throughout our academic journey.

To our thesis mates, \textbf{\textit{Merajul}}, \textbf{\textit{May-Ann}}, \textbf{\textit{Kyrstine}}, and \textbf{\textit{Trishia}}, for sharing your laughter and wonderful moments with us. The sleepless nights and tiring days are finally over, but they were all worth it.

To our friends for your prayers and moral support. You all made this journey worthy of remembering.

To our families, for your unceasing love, moral and financial support. All of you are our inspirations who constantly reminded us not to give up amidst difficulties and uncertainties.

And to those people we failed to mention, who directly or indirectly lent their hands, extended their prayers and support for the completion of this study. 

Above all, to \textbf{\textit{Almighty God}}, whose unconditional love infinitely transcends all human comprehension, for providing us with good health, divine protection and bountiful blessings.

\begin{flushright}
\textbf{\textit{Researchers}}
\end{flushright}



}